### 2025-08-22 sec/evaluation.tex
Figures side by side.

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.95\linewidth]{fig/success_rate_by_category}
    \caption{Success rate by testcases}\label{fig:success_rate_by_category}
\end{figure}

>>>>

\begin{figure}
    \centering
    \begin{subfigure}{0.48\linewidth}
        \centering
        \includegraphics[width=\linewidth]{fig/success_rate_by_category}
        \caption{Success rate by testcases}
        \label{fig:success_rate_by_category}
    \end{subfigure}\hfill
    \begin{subfigure}{0.48\linewidth}
        \centering
        \includegraphics[width=\linewidth]{fig/success_rate_by_category_count}
        \caption{Success rate by category count}
        \label{fig:success_rate_by_category_count}
    \end{subfigure}
    \caption{Comparison of success rates}
    \label{fig:success_rate_comparison}
\end{figure}
